---
title: "615 Shiny"
author: "Yiming Chen"
date: "2024-11-12"
output:
  html_document:
    df_print: paged
  pdf_document: default
runtime: shiny
---
```{r}
library(shiny)
```

#Hadley_1
```{r}
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)


server <- function(input, output, session) {
  output$summary <- renderPrint({
    dataset <- get(input$dataset, "package:datasets")
    summary(dataset)
  })
  
  output$table <- renderTable({
    dataset <- get(input$dataset, "package:datasets")
    dataset
  })
}

shinyApp(ui, server)
```

#Hadley_2
```{r}
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)

server <- function(input, output, session) {
  # Create a reactive expression
  dataset <- reactive({
    get(input$dataset, "package:datasets")
  })

  output$summary <- renderPrint({
    # Use a reactive expression by calling it like a function
    summary(dataset())
  })
  
  output$table <- renderTable({
    dataset()
  })
}
shinyApp(ui, server)
```

# 2.3.5 Exercises
## 1.
a.verbatimTextOutput()
b.textOutput()
c.verbatimTextOutput()
d.textOutput()

## 2.
__height:300px, width:700px__
```{r}
library(shiny)

ui <- fluidPage(
  plotOutput("plot", height = "300px", width = "700px")
)
server <- function(input, output, session) {
  output$plot <- renderPlot({
    plot(1:5, rnorm(5), main = "Scatterplot of Five Random Numbers")
  }, res = 96)
}
#server <- function(input, output, session) {
 # output$plot <- renderPlot(plot(1:5), res = 96)
#}
shinyApp(ui, server)
```

## 3.

```{r}
ui <- fluidPage(
  dataTableOutput("table")
)

server <- function(input, output, session) {
  output$table <- DT::renderDT(mtcars, options = list(pageLength = 5))
}

shinyApp(ui, server)

```

## 4.
```{r}
library(reactable)

ui <- fluidPage(
  reactableOutput("table")
)

server <- function(input, output, session) {
  output$table <- renderReactable({
    reactable(
      mtcars,
      pagination = TRUE,          # Enable pagination
      searchable = FALSE,         # Disable the search box
      sortable = FALSE,           # Disable column sorting
      showPageSizeOptions = FALSE # Disable option to change number of rows displayed
    )
  })
}

shinyApp(ui, server)

```

# 3.3.6 Exercises
## 1.
```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
```
__server1__
```{r}
server1 <- function(input, output, server) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
```
__server2__
```{r}
server2 <- function(input, output, server) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
```
__server3__
```{r}
server3 <- function(input, output, server) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
```
## 2.
__server1__
```{r}
server1 <- function(input, output, session) {
  c <- reactive(input$a + input$b)
  e <- reactive(c() + input$d)
  output$f <- renderText(e())
}
```
__server2__
```{r}
server2 <- function(input, output, session) {
  x <- reactive(input$x1 + input$x2 + input$x3)
  y <- reactive(input$y1 + input$y2)
  output$z <- renderText(x() / y())
}

```
__server3__
```{r}
server3 <- function(input, output, session) {
  d <- reactive(c() ^ input$d)
  a <- reactive(input$a * 10)
  c <- reactive(b() / input$c)
  b <- reactive(a() + input$b)
}
```

```{r}
# Load necessary packages
library(DiagrammeR)

# Define the graphs for each server function

# Graph for server1
graph_server1 <- grViz("
digraph server1 {
  'input$a' -> 'c'
  'input$b' -> 'c'
  'c' -> 'e'
  'input$d' -> 'e'
  'e' -> 'output$f'
}
")

# Graph for server2
graph_server2 <- grViz("
digraph server2 {
  'input$x1' -> 'x'
  'input$x2' -> 'x'
  'input$x3' -> 'x'
  'x' -> 'output$z'
  'input$y1' -> 'y'
  'input$y2' -> 'y'
  'y' -> 'output$z'
}
")

# Graph for server3
graph_server3 <- grViz("
digraph server3 {
  'input$a' -> 'a'
  'a' -> 'b'
  'input$b' -> 'b'
  'b' -> 'c'
  'input$c' -> 'c'
  'c' -> 'd'
  'input$d' -> 'd'
}
")

# Display the graphs
graph_server1
graph_server2
graph_server3

```

## 3.
```{r}
selected_var <- reactive(df[[input$var]])
var_range <- reactive(range(selected_var(), na.rm = TRUE))
```
The code fails because "var" and "range" are names of existing R functions. var() for variance and range() for the range of a vector. Using them as reactive names can cause conflicts and make the code unclear.

# 4.8 Exercises
## 1.

                    ┌───────────────┐
                    │ input$code    │
                    └──────┬────────┘
                           │
                 ┌─────────▼───────────┐
                 │ selected()          │
                 │ (filters injuries   │
                 │  based on prod_code)│
                 └───┬──────────┬──────┘
                     │          │
        ┌────────────▼───┐ ┌────▼────────────┐
        │ output$diag    │ │ output$body_part│
        │ (table count   │ │ (table count    │
        │  by diag)      │ │  by body_part)  │
        └────────────────┘ └─────────────────┘
                      │
                      │
                  ┌───▼───────────────┐
                  │ output$location   │
                  │ (table count      │
                  │  by location)     │
                  └───▲───────────────┘
                      │
              ┌───────┴───────────────┐
              │ summary()             │
              │ (count by age, sex,   │
              │  then joined with     │
              │  population)          │
              └─────────┬─────────────┘
                        │
             ┌──────────▼────────────┐
             │ output$age_sex        │
             │ (line plot by age,    │
             │  n per age-sex group) │
             └────────────────────────┘




                    ┌───────────────┐
                    │ input$code    │
                    └──────┬────────┘
                           │
                 ┌─────────▼───────────┐
                 │ selected()          │
                 │ (filters injuries   │
                 │  based on prod_code)│
                 └───┬──────────┬──────┘
                     │          │
        ┌────────────▼───┐ ┌────▼────────────┐
        │ output$diag    │ │ output$body_part│
        │ (table count   │ │ (table count    │
        │  by diag)      │ │  by body_part)  │
        └────────────────┘ └─────────────────┘
                      │
                      │
                  ┌───▼───────────────┐
                  │ output$location   │
                  │ (table count      │
                  │  by location)     │
                  └───▲───────────────┘
                      │
              ┌───────┴───────────────┐
              │ summary()             │
              │ (count by age, sex,   │
              │  then joined with     │
              │  population)          │
              └─────────┬─────────────┘
                        │
          ┌─────────────▼────────────────────────────┐
          │ input$y                                 │
          │ (user choice: rate vs count)            │
          └─────────────┬───────────────────────────┘
                        │
             ┌──────────▼────────────┐
             │ output$age_sex        │
             │ (conditional plot by  │
             │  age: rate or count   │
             │  based on input$y)    │
             └────────────────────────┘




                    ┌───────────────┐
                    │ input$code    │
                    └──────┬────────┘
                           │
                 ┌─────────▼───────────┐
                 │ selected()          │
                 │ (filters injuries   │
                 │  based on prod_code)│
                 └───┬──────────┬──────┘
                     │          │
        ┌────────────▼───┐ ┌────▼────────────┐
        │ output$diag    │ │ output$body_part│
        │ (table count   │ │ (table count    │
        │  by diag)      │ │  by body_part)  │
        └────────────────┘ └─────────────────┘
                      │
                      │
                  ┌───▼───────────────┐
                  │ output$location   │
                  │ (table count      │
                  │  by location)     │
                  └───▲───────────────┘
                      │
              ┌───────┴───────────────┐
              │ summary()             │
              │ (count by age, sex,   │
              │  then joined with     │
              │  population)          │
              └─────────┬─────────────┘
                        │
             ┌──────────▼────────────┐
             │ output$age_sex        │
             │ (conditional plot by  │
             │  age: rate or count)  │
             └──────────┬────────────┘
                        │
             ┌──────────▼────────────┐
             │ input$story           │
             └──────────┬────────────┘
                        │
            ┌───────────▼─────────────┐
            │ narrative_sample()      │
            │ (gets new narrative     │
            │  on button click)       │
            └───────────┬─────────────┘
                        │
              ┌─────────▼──────────────┐
              │ output$narrative       │
              │ (displays current      │
              │  narrative text)       │
              └────────────────────────┘







## 2.
If you reverse the order of fct_infreq() and fct_lump(), the code will first lump all values and then order them by frequency. This approach may result in a less accurate summary table, as less common factors could be grouped together with more common ones. This can reduce the interpretability and accuracy of the summarized data.

## 3.
__Add a slider input for selecting the number of rows to display__
column(4, 
       sliderInput("num_rows", 
                   label = "Number of rows:", 
                   min = 1, 
                   max = 10, 
                   value = 5))

__Render tables for diagnosis, body part, and location, showing the top rows based on the selected number__
output$diag <- renderTable({
  count_top(selected(), diag, n = input$num_rows)
}, width = "100%")

output$body_part <- renderTable({
  count_top(selected(), body_part, n = input$num_rows)
}, width = "100%")

output$location <- renderTable({
  count_top(selected(), location, n = input$num_rows)
}, width = "100%")


## 4.
```{r}
fluidRow(
  column(1, actionButton("prev_story", "Previous")),
  column(1, actionButton("next_story", "Next")),
  column(10, textOutput("narrative"))
)
```

__Reactive value to track the current narrative index__
narrative_index <- reactiveVal(1)

__Update the narrative index when the "Next Story" button is clicked__
observeEvent(input$next_story, {
  current <- narrative_index()
  narrative_index(min(current + 1, nrow(selected())))
})

__Update the narrative index when the "Previous Story" button is clicked__
observeEvent(input$prev_story, {
  current <- narrative_index()
  narrative_index(max(current - 1, 1))
})

__Render the current narrative text based on the narrative index__
output$narrative <- renderText({
  selected() %>%
    pull(narrative) %>%
    .[narrative_index()]
})


